LEGWORK: A python package for computing the evolution and detectability \\ of stellar-origin gravitational-wave sources with space-based detectors

### 2022-08-04 src/tex/ms.tex
remove erroneous factors of 1/4
update to latest LEGWORK version before arXiv upload

For a evolving and circular binary, the sum can be removed and so the SNR found as
\begin{equation}{\lwFuncURL{snr}{snr_circ_evolving}}
    \referee{\langle \rho \rangle^2_{\rm c, e}} = \frac{1}{4} \int_{f_{2, i}}^{f_{2, f}} \frac{h_{c, 2}^2}{f_2^2 S_{\rm n}(f_2)} \dd{f_2}. \label{eq:snr_chirp_circ}
\end{equation}

For a stationary and eccentric binary we can approximate the integral.
\begin{align}
    \referee{\langle \rho \rangle^2_{\rm e, s}} &= \frac{1}{4} \sum_{n=1}^{\infty}  \lim_{\Delta f \to 0} \int_{f_{n}}^{f_{n} + \Delta f_n} \frac{h_{c, n}^2}{f_n^2 S_{\rm n}(f_n)} \dd{f_n}, \\
    &= \frac{1}{4} \sum_{n=1}^{\infty} \frac{\Delta f_n \cdot h_{c, n}^2}{f_n^2 S_{\rm n}(f_n)}, \\
    &= \frac{1}{4} \sum_{n=1}^{\infty} \frac{\dot{f}_n \Delta T \cdot h_{c, n}^2}{f_n^2 S_{\rm n}(f_n)}, \\
    &= \frac{1}{4} \sum_{n=1}^{\infty} \qty(\frac{\dot{f}_n}{f_n^2} h_{c, n}^2) \frac{T_{\rm obs}}{S_{\rm n}(f_n)},
\end{align}
where we have applied \eqref{eq:strain-charstrain} to convert between strains. This gives the following expression
\begin{equation}{\lwFuncURL{snr}{snr_ecc_stationary}}
    \referee{\langle \rho \rangle^2_{\rm e, s}} = \frac{1}{4} \sum_{n=1}^{\infty} \frac{h_{n}^2 T_{\rm obs}}{S_{\rm n}(f_n)}. \label{eq:snr_stat_ecc}
\end{equation}
Finally, for a stationary and circular binary the signal-to-noise ratio is
\begin{equation}{\lwFuncURL{snr}{snr_circ_stationary}}
    \referee{\langle \rho \rangle^2_{\rm c, s}} = \frac{1}{4} \frac{h_2^2 T_{\rm obs}}{S_{\rm n}(f_2)}.
    \label{eq:snr_stat_circ}
\end{equation}

For SNR calculations that take into account the amplitude modulation due to LISA's orbital motion (Section~\ref{sec:amplitude_mod}, we apply the calculations as described above but include the modulation in either the strain or characteristic strain as is appropriate.

>>>>

For a evolving and circular binary, the sum can be removed and so the SNR found as
\begin{equation}{\lwFuncURL{snr}{snr_circ_evolving}}
    \referee{\langle \rho \rangle^2_{\rm c, e}} = \int_{f_{2, i}}^{f_{2, f}} \frac{h_{c, 2}^2}{f_2^2 S_{\rm n}(f_2)} \dd{f_2}. \label{eq:snr_chirp_circ}
\end{equation}
For a stationary and eccentric binary we can approximate the integral.
\begin{align}
    \referee{\langle \rho \rangle^2_{\rm e, s}} &= \sum_{n=1}^{\infty}  \lim_{\Delta f \to 0} \int_{f_{n}}^{f_{n} + \Delta f_n} \frac{h_{c, n}^2}{f_n^2 S_{\rm n}(f_n)} \dd{f_n}, \\
    &= \sum_{n=1}^{\infty} \frac{\Delta f_n \cdot h_{c, n}^2}{f_n^2 S_{\rm n}(f_n)}, \\
    &= \sum_{n=1}^{\infty} \frac{\dot{f}_n \Delta T \cdot h_{c, n}^2}{f_n^2 S_{\rm n}(f_n)}, \\
    &= \sum_{n=1}^{\infty} \qty(\frac{\dot{f}_n}{f_n^2} h_{c, n}^2) \frac{T_{\rm obs}}{S_{\rm n}(f_n)},
\end{align}
where we have applied Eq.~\ref{eq:strain-charstrain} to convert between strains. This gives the following expression
\begin{equation}{\lwFuncURL{snr}{snr_ecc_stationary}}
    \referee{\langle \rho \rangle^2_{\rm e, s}} = \sum_{n=1}^{\infty} \frac{h_{n}^2 T_{\rm obs}}{S_{\rm n}(f_n)}. \label{eq:snr_stat_ecc}
\end{equation}
Finally, for a stationary and circular binary the signal-to-noise ratio is
\begin{equation}{\lwFuncURL{snr}{snr_circ_stationary}}
    \referee{\langle \rho \rangle^2_{\rm c, s}} = \frac{h_2^2 T_{\rm obs}}{S_{\rm n}(f_2)}.
    \label{eq:snr_stat_circ}
\end{equation}
For SNR calculations that take into account the amplitude modulation due to LISA's orbital motion (Section~\ref{sec:amplitude_mod}, we apply the calculations as described above but include the modulation in either the strain or characteristic strain as is appropriate.
